\documentclass[conference]{IEEEtran}
\input{preamble}

\begin{document}

% ── Title block ───────────────────────────────────────────────────────────────
\title{Empirical L\'{e}vy Scaling in Short-Horizon Futures Returns:
       Estimation, Sensitivity, and Autocorrelation Bias}

\author{\IEEEauthorblockN{Haoping Qiu}
\IEEEauthorblockA{\textit{[Department]}\\
\textit{[University]}\\
\mbox{[City, Country]}\\
\mbox{[email]}}}

% ══════════════════════════════════════════════════════════════════════════════
\maketitle
% ══════════════════════════════════════════════════════════════════════════════

% ── Abstract ──────────────────────────────────────────────────────────────────
\begin{abstract}
Short-horizon price increments in equity-index futures exhibit heavy tails and
a sharply peaked central body inconsistent with Gaussian dynamics, motivating
Lévy-stable distributional models with characteristic exponent
$\alpha\in(1,2)$.
This paper examines Lévy scaling across eight equity-index futures contracts
spanning North America and Europe using 1-minute OHLCV data from exchange
inception through January 2026.
Three estimation approaches (peak-scaling OLS, collapse-quality
minimisation, and fractional-order structure functions) are applied across
a full-factorial robustness matrix spanning histogram resolution, lag-grid
density, and intraday seasonality correction.
Seven of the eight markets yield peak-scaling exponents
$\hat\alpha_{\mathrm{tip}}\in(1.73,\,1.84)$ with $R^2>0.99$, consistent with
the truncated Lévy-flight consensus.
The S\&P/TSX~60 contract is a persistent outlier ($\hat\alpha\approx 2.6$),
attributable to low liquidity and excess zero increments.
The estimator choice, not tuning parameters, is the dominant source of
variation in reported exponents; inter-estimator spreads of $0.15$--$0.35$
units exceed the inter-market range for the seven conforming contracts.
Seven of the eight markets exhibit negative first-order autocorrelation
and one (ER) a marginally positive value, all violating the
i.i.d.\ assumption underlying peak-scaling.
A closed-form variance-ratio bias correction reduces $\hat\alpha$ by
$0.04$--$0.92$ units for seven of the eight markets; the sole exception (ER)
has marginally positive first-order autocorrelation and corrects upward by
$0.04$ units.
The correction magnitude is monotonically ordered by variance ratio across
the seven mean-reverting markets, providing a cross-sectional validation of
the bias mechanism.
\end{abstract}

\begin{IEEEkeywords}
Lévy-stable distributions, peak-scaling estimator, equity-index futures,
variance ratio, intraday returns, self-similarity.
\end{IEEEkeywords}

% ══════════════════════════════════════════════════════════════════════════════
\section{Introduction}
\label{sec:intro}
% ══════════════════════════════════════════════════════════════════════════════

The distributional properties of short-horizon price changes have been a
central concern of financial economics and econophysics since at least
Bachelier \cite{Bachelier1900}. The Gaussian random-walk model, which predicts
normally distributed increments and variance scaling linearly with the holding
period, is a natural first approximation but a poor empirical description of
intraday returns. High-frequency data reveal distributions with heavy tails,
excess kurtosis, and a central body that is far more peaked than the Gaussian.
These features, documented across equities, foreign exchange, and derivatives
markets, motivate the use of Lévy-stable distributions as a richer
distributional model \cite{Mandelbrot1963,MantegnaStanley1994,Cont2001}.

The central prediction of the symmetric $\alpha$-stable model is
\textit{self-similarity}: the distribution of $\tau$-step price increments is
a rescaled version of the one-step distribution, with the scale factor growing
as $\tau^{1/\alpha}$ for a characteristic exponent $\alpha\in(1,2)$. This
implies, in particular, that the peak of the empirical probability density
decays as $P(0,\tau)\propto\tau^{-1/\alpha}$, a relation that can be estimated
by ordinary least squares on a log-log plot and that forms the basis of the
\textit{peak-scaling} approach of Mantegna and Stanley \cite{MantegnaStanley1994,MantegnaStanley1995}.
The same self-similarity predicts that empirical PDFs at different lags, when
rescaled by $\tau^{1/\alpha}$, should collapse onto a common curve, providing
a qualitative visual test of the Lévy hypothesis. Both the regression and the
collapse have been applied extensively in the econophysics literature, with
estimated exponents consistently falling in the range $\alpha\approx 1.5$--$1.9$
\cite{Gopikrishnan1999,Weron2001,BouchaudPotters2003}.

Despite this activity, three important gaps remain. First, most existing
studies focus on a single market or a narrow class of instruments, typically
US equity indices or individual stocks, and it is unclear how far the
$\alpha\approx 1.7$--$1.8$ consensus extends to a focused cross-section of
eight liquid equity-index futures contracts across different geographies and
regulatory environments. Second, the sensitivity of $\alphah$ to methodological
choices including histogram resolution, lag grid density, intraday
seasonality removal, and estimator selection has not been systematically
quantified in a single study; different choices can shift estimates by
amounts that matter for practical inference. Third, and most substantively,
the peak-scaling estimator is derived under the assumption of independent
increments, yet 1-minute futures returns exhibit well-documented short-term
mean reversion driven by the bid-ask bounce and order-book dynamics
\cite{Roll1984,Bouchaud2004}. The direction of the resulting bias is
known qualitatively \cite{BouchaudPotters2003}, but no closed-form
correction has been derived and validated empirically.

This paper addresses all three gaps. Using 1-minute OHLCV data for eight
equity-index futures contracts spanning North America and Europe, sourced from
OneTick via TickData and covering each contract from exchange inception through
January 2026, we make six contributions organized around the three gaps.

\textit{Addressing gap 1 (cross-market coverage):}
(i)~We establish a baseline peak-scaling survey across all eight markets,
reporting $\alphah_{\mathrm{tip}}$ and collapse diagnostics for each.
(v)~We test the symmetry assumption of the Lévy model by computing the
pointwise asymmetry of the empirical PDFs and examining whether symmetrization
improves collapse quality.

\textit{Addressing gap 2 (methodological sensitivity):}
(ii)~We test the effect of intraday seasonality removal on $\alphah$, running
the full PDF analysis on both raw and de-seasonalized price series and
comparing the resulting estimates.
(iii)~We compare three independent estimators (tip-scaling OLS,
collapse-quality minimization, and fractional-order structure functions)
across all markets to assess their mutual consistency.
(iv)~We construct a full-factorial robustness matrix spanning all combinations
of histogram resolution, lag-grid density, preprocessing choice, and
estimator, and decompose the variance of $\alphah$ across these factors to
identify which choices matter most.

\textit{Addressing gap 3 (bias correction):}
(vi)~We derive a closed-form bias correction for the peak-scaling estimator
under short-term mean reversion, express it in terms of the
Campbell--Lo--MacKinlay variance ratio, and validate the correction across
all eight markets.

The paper is organized as follows. Section~\ref{sec:background} provides
the theoretical background on Lévy-stable distributions, peak-scaling
estimation, and the variance-ratio framework. Section~\ref{sec:data} describes
the data and preprocessing steps. Section~\ref{sec:methodology} develops the
six analytical methods in detail. Section~\ref{sec:results} presents the
results for each contribution. Section~\ref{sec:conclusion} summarizes the
findings, discusses limitations, and suggests extensions.


% ══════════════════════════════════════════════════════════════════════════════
\section{Background}
\label{sec:background}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{Lévy-stable distributions and the peak-scaling formula}
\label{sec:background:levy}

The Lévy-Khintchine theorem establishes that the class of stable distributions
is the complete set of non-trivial distributional limits of normalized sums of
i.i.d.\ random variables \cite{SamorodTaqqu1994,GnedenkoKolmogorov1954}.
A symmetric $\alpha$-stable variable $X \sim S_\alpha(\gamma,0,0)$ has
characteristic function
\begin{equation}
  \Etau\!\left[e^{iqX}\right] = \exp\!\left(-\gamma|q|^\alpha\right),
  \quad \gamma > 0,\quad \alpha \in (0,2].
  \label{eq:cf}
\end{equation}
The Gaussian ($\alpha = 2$) is the unique finite-variance special case; for
$\alpha < 2$ the tails decay algebraically as $P(|X|>u)\sim C_\alpha u^{-\alpha}$,
so all moments of order $\geq\alpha$ are infinite.

For i.i.d.\ increments drawn from $S_\alpha(\gamma_1,0,0)$, the $\tau$-step sum
has scale $\gamma = \gamma_1^\alpha\tau$, yielding the self-similarity property
\begin{equation}
  P_{\alpha,\gamma}(x,\tau)
  = (\gamma\tau)^{-1/\alpha}
    F_\alpha\!\left(\frac{x}{(\gamma\tau)^{1/\alpha}}\right),
  \label{eq:scaling}
\end{equation}
where $F_\alpha$ is the standardized stable density. This scaling form is the
central prediction of the Lévy model: the shape of the increment distribution
is identical at every lag, up to a scale factor growing as $\tau^{1/\alpha}$.
Setting $x=0$ and using $F_\alpha(0) = \Gamma(1/\alpha)/(\pi\alpha)$ gives the
\textit{peak-scaling formula}
\begin{equation}
  P(0,\tau)
  = \frac{\Gamma(1/\alpha)}{\pi\alpha}\,(\gamma\tau)^{-1/\alpha}.
  \label{eq:peak}
\end{equation}
The log-log regression of $\Ph(0,\tau)$ on $\tau$ therefore has slope
$-1/\alpha$, independent of the scale parameter $\gamma$.

Mandelbrot \cite{Mandelbrot1963} first proposed that asset-price increments lie in
the domain of attraction of a stable law with $\alpha\in(1,2)$.
Mantegna and Stanley \cite{MantegnaStanley1994,MantegnaStanley1995} provided the first
systematic intraday evidence using S\&P 500 data, finding $\alpha\approx 1.4$
over three orders of magnitude in lag and demonstrating clean PDF collapse.
The truncated Lévy flight (TLF) resolves the tension between
infinite-variance stable laws and finite empirical moments: the distribution
follows the stable power law over intermediate scales but is exponentially
cut off in the far tail, producing finite variance while preserving
Lévy-like body scaling over the observable range
\cite{MantegnaStanley1994,BouchaudPotters2003}. Weron \cite{Weron2001}
showed that samples of $10^6$ or more are required before the true stable tail
emerges, far beyond the practical size of intraday datasets, so empirical
$\alphah$ estimates are best interpreted as body-scaling parameters rather
than tail-index claims.

Gopikrishnan et al.\ \cite{Gopikrishnan1999} extended the analysis to individual US stocks and
found power-law tails with exponent $\zeta\approx 3$, outside the Lévy-stable
regime in the strict sense. Weron \cite{Weron2001} showed this apparent
discrepancy is a finite-sample artifact: a Lévy-stable distribution with
$\alpha\approx 1.7$-$1.8$ produces Hill-estimator values of $\zeta\approx 3$
on samples of realistic size. This reconciliation motivates the
multi-estimator approach used here and the conservative
interpretation of $\alphah$ as a central-body parameter. More recent work by
Masoliver and Perelló \cite{Masoliver2021} and Cont et al.\ \cite{ContMiami2023} confirms that the
central-body Lévy-scaling picture is stable through the 2010s, justifying its
application to contemporary futures data.

\subsection{Estimation of the scaling exponent}
\label{sec:background:estimation}

Three estimation strategies are employed.

The \textit{peak-scaling OLS} estimator, introduced by
Mantegna and Stanley \cite{MantegnaStanley1994}, regresses $\log\Ph(0,\tau)$ on $\log\tau$ and
recovers $\alphah_{\mathrm{tip}} = -1/\hat{m}$ from the slope $\hat{m}$.
The estimator is semi-parametric: it uses only the value of the distribution
at the origin and makes no assumption about the shape elsewhere.

The \textit{collapse-quality} estimator \cite{Drozdz2003} chooses
$\alpha$ to minimize the spread of the rescaled empirical curves
$\tau^{1/\alpha}\Ph(\tau^{1/\alpha}\tilde{x},\tau)$ around a common function.
A mean-squared log-deviation score weights the central body and the tails
more evenly than a pure-origin regression, providing an independent route to
$\alphah$ that does not rely on a single histogram bin.

The \textit{fractional structure function} estimator
\cite{MuzyBacry1993,BouchaudPotters2003} exploits the prediction
$S_q(\tau) = \Etau[|\Delta P_\tau|^q] \propto \tau^{q/\alpha}$ for $q <
\alpha$. A log-log regression of $\hat{S}_q(\tau)$ on $\tau$ yields
slope $q/\alphah_q$; the median across moment orders
$q\in\{0.25,0.5,0.75,1.0,1.25,1.5\}$ gives $\alphah_{\mathrm{sf}}$.
Fractional orders $q\in(0,1)$ downweight outliers and converge reliably on
moderate samples \cite{Uchaikin2003}, while $q\in(1,\alpha)$ are
sensitive to the tail. Systematic concavity of the empirical scaling exponent
$\hat\zeta(q) = q/\alphah_q$ would signal multifractal corrections beyond
simple Lévy scaling \cite{Mandelbrot1997,MuzyBacry1993}.

Weron \cite{Weron2001} and Baru\v{n}\'ik and Va\v{c}ha \cite{Barunik2010} document that all three of
these semi-parametric methods outperform the Hill estimator for $\alpha$ near
2 on finite samples. The comparison of the three estimators across all eight
markets is central to the robustness analysis of Section~\ref{sec:results:robustness}.

\subsection{Short-term dependence and the variance-ratio bias}
\label{sec:background:vr}

Lo and MacKinlay \cite{LoMacKinlay1988} introduced the variance ratio
\begin{equation}
  VR(\tau) = \frac{\mathrm{Var}(\Delta P_\tau)}{\tau\,\mathrm{Var}(\delta_1)},
  \label{eq:vr}
\end{equation}
which equals 1 under i.i.d.\ increments, exceeds 1 under positive serial
correlation, and falls below 1 under mean reversion. The exact relationship
to the autocorrelation function is
\begin{equation}
  VR(\tau)
  = 1 + 2\sum_{k=1}^{\tau-1}\!\left(1-\frac{k}{\tau}\right)\rho(k),
  \label{eq:vr_rho}
\end{equation}
which forms the basis for both variance-ratio estimators implemented in the
notebook.

At 1-minute frequency the dominant effect is mean reversion, not the positive
correlation found at weekly horizons by Lo and MacKinlay \cite{LoMacKinlay1988}. Two
mechanisms contribute. Roll \cite{Roll1984} showed that bid-ask bounce
generates spurious first-order autocorrelation $\rhoh(1)\approx -s^2/4$ for
effective spread $s$, a purely mechanical effect. Bouchaud et al.\ \cite{Bouchaud2004} and
Farmer et al.\ \cite{Farmer2006} documented that large market orders move prices but
this impact partially reverts as the order book replenishes, adding genuine
mean reversion at short horizons. Bouchaud and Potters \cite{BouchaudPotters2003} (Ch.~6)
report $\rhoh(1)\approx -0.1$ to $-0.2$ at 1-minute frequency in major
equity index futures, consistent with the values reported here.

The canonical peak formula~\eqref{eq:peak} is derived under strictly
independent increments. When $VR(\tau)\neq 1$, the effective Lévy scale at
lag $\tau$ is modified. The derivation proceeds in two steps.
First, by the definition of the variance ratio in Equation~\eqref{eq:vr},
the spread of $\Delta P_\tau$ under correlated increments satisfies
$\mathrm{Var}(\Delta P_\tau)=\tau\,\mathrm{Var}(\delta_1)\cdot VR(\tau)$,
i.e., the ``dispersion'' of the $\tau$-step sum is scaled by $\sqrt{VR(\tau)}$
relative to the i.i.d.\ baseline.
Second, for a symmetric $\alpha$-stable distribution the scale parameter
$\gamma$ transforms as $\gamma\mapsto c^\alpha\gamma$ under a linear scaling
$X\mapsto cX$ (homogeneity of the stable CF); hence scaling the dispersion
by $\sqrt{VR(\tau)}$ scales $\gamma$ by $(\sqrt{VR(\tau)})^\alpha
= VR(\tau)^{\alpha/2}$.
Combining, the effective Lévy scale at lag $\tau$ is
\begin{equation}
  \gamma_{\mathrm{eff}}(\tau) = \gamma\tau\cdot VR(\tau)^{\alpha/2},
  \label{eq:gamma_eff}
\end{equation}
and substituting into Equation~\eqref{eq:peak} gives the corrected
log-peak regression
\begin{equation}
  \log P(0,\tau)
  = -\frac{1}{\alpha}\log\tau
    - \frac{1}{2}\log VR(\tau)
    + \mathrm{const}.
  \label{eq:corrected_peak}
\end{equation}
For a mean-reverting process ($VR(\tau)<1$) the omission of the second term
causes the raw OLS slope to underestimate $-1/\alpha$ in magnitude, biasing
$\alphah_{\mathrm{tip}}$ upward toward the Gaussian boundary. The correction
procedure is developed in Section~\ref{sec:methodology:bias}. To our knowledge, the explicit OLS bias formula in the
Campbell--Lo--MacKinlay variance-ratio form and its cross-market empirical
validation have not been jointly reported; Bouchaud and Potters \cite{BouchaudPotters2003}
(Ch.~6) discuss the qualitative direction of the effect but do not derive
the specific correction term or validate it across a cross-section of markets.


% ══════════════════════════════════════════════════════════════════════════════
\section{Data}
\label{sec:data}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{Markets and sample}
\label{sec:data:markets}

The dataset consists of 1-minute resolution day-session price histories for
eight equity-index futures contracts spanning four geographical regions. The
data were provided by Prof.\ Alexei Chekhlov and sourced from OneTick via
TickData, covering each contract from its
exchange inception through 14 January 2026. Table~\ref{tab:markets} provides
a full description of each contract.

\begin{table*}[htbp]
\begin{center}
\caption{Sample Futures Contracts}
\begin{tabular}{llllll}
\hline
Symbol & Name & Region & Exchange & History Start & Session \\
\hline
YM & Dow Jones E-mini      & Americas & CBOT/CME           & May 2002    & 08:30--15:15 \\
NQ & NASDAQ 100 E-mini     & Americas & CME                & Jul 1999    & 08:30--15:15 \\
ER & Russell 2000 E-mini   & Americas & CBOT/CME           & Jan 2002    & 08:30--15:15 \\
ES & S\&P 500 E-mini       & Americas & CME                & Sep 1997    & 08:30--15:15 \\
PT & S\&P Canada 60        & Americas & Montreal SE        & Oct 1999    & 09:30--16:15 \\
FT & FTSE 100              & Europe   & ICE Futures        & Jul 1998    & 08:00--16:30 \\
DA & DAX                   & Europe   & EUREX              & Jan 1997    & 09:00--17:30 \\
CF & CAC-40                & Europe   & Euronext           & May 2000    & 09:00--17:30 \\
\hline
\end{tabular}
\label{tab:markets}
\end{center}
\end{table*}

The eight contracts were selected to provide a focused cross-section of
liquid equity-index futures across geographies rather than on the basis of
any statistical pre-screening. Three North American equity-index contracts (YM, NQ, ER, ES)
trade on CME Group venues; one Canadian contract (PT) trades on the Montreal
Stock Exchange; and three European contracts (FT, DA, CF) cover the major
continental and UK equity benchmarks.

The raw files are stored in ``skip'' format: minutes with no transactions are
omitted from the file rather than recorded as zero-volume observations. This
is addressed in preprocessing (Section~\ref{sec:data:preprocessing}).

To justify the use of 1-minute price changes as the elementary increment,
Table~\ref{tab:sigma} reports the standard deviation of 1-minute price
changes $\sigma_1$ and the average bid-ask spread $\Delta$ for each market.
A necessary condition for 1-minute returns to carry genuine price information
is $\sigma_1 / \Delta > 1$; otherwise a substantial fraction of observed
changes reflects the bid-ask bounce rather than true price movement
\cite{Roll1984}. As the ratio $\sigma_1/\Delta$ exceeds 1 for all eight
markets, the 1-minute frequency is appropriate.

\begin{table}[htbp]
\begin{center}
\caption{Market Volatility and Bid-Ask Spread}
\begin{tabular}{lrrr}
\hline
Market & $\sigma_1$ & $\Delta$ (bid-ask) & $\sigma_1/\Delta$ \\
\hline
YM & 6.15 & 1.30 & 4.73 \\
NQ & 2.33 & 0.48 & 4.90 \\
ER & 0.51 & 0.22 & 2.32 \\
ES & 0.68 & 0.25 & 2.71 \\
PT & 2.78 & 2.50 & 1.11 \\
FT & 3.48 & 1.20 & 2.90 \\
DA & 2.61 & 2.00 & 1.31 \\
CF & 0.46 & 0.22 & 2.09 \\
\hline
\end{tabular}
\label{tab:sigma}
\end{center}
\end{table}

\subsection{Preprocessing}
\label{sec:data:preprocessing}

Three preprocessing steps are applied uniformly across all markets before any
statistical analysis.

\textbf{Integer-scale conversion.} Raw prices are quoted in their native tick
units. To work in integer arithmetic and avoid floating-point accumulation
errors, each price series is multiplied by the contract-specific scaling
factor $1/\Delta$ and rounded to the nearest integer, so that one tick
corresponds to one integer unit. All subsequent price differences are
therefore integer-valued.

\textbf{Gap-filling.} The raw files omit minutes with no transactions. Missing
minutes within a trading session are filled by carrying forward the last
observed price (last-observation-carried-forward, LOCF). This preserves the
equal-spacing of the 1-minute grid required for the lag-$\tau$ increment
construction while recording zero price change during illiquid periods, which
is consistent with the true mid-price behavior in the absence of transactions.

\textbf{Lag grid construction.} Price increments $\delta_\tau(t) = P(t) -
P(t-\tau)$ are formed for each lag $\tau$ on two log-spaced grids. The coarse
grid ($N_\tau = 20$) spans $\tau \in \{1, 2, 3, 6, \ldots, 56{,}234\}$
minutes; the fine grid ($N_\tau = 37$) spans the same range with higher
density. The maximum lag of 56,234 minutes corresponds to approximately six
months of trading for a 405-minute session, well beyond the scale at which
convergence to Gaussian behavior is expected. Both grids are used in all
estimations to assess the sensitivity of $\alphah$ to the choice of $N_\tau$.


\subsection{Empirical PDF estimation}
\label{sec:methodology:pdf}

For each market and lag $\tau$ on the grid, price increments
$\Delta P_\tau(t) = P(t) - P(t-\tau)$ are formed from the gap-filled
integer-scaled price series. The histogram bin width is $\Delta x = \varepsilon
\cdot \Delta$, where $\Delta$ is the bid-ask spread in tick units and
$\varepsilon$ is a dimensionless resolution parameter. The normalised histogram
density is
\begin{equation}
  \Ph(x_j,\tau)
  = \frac{\#\{i: \Delta P_\tau(t_i)\in\text{bin }j\}}{N_\tau\cdot\Delta x},
  \label{eq:pdf_hat}
\end{equation}
where $N_\tau$ is the number of available increments. The bin half-width
$x_{\max}$ is set to cover the bulk of the distribution while maintaining
$N_x = 2{,}000$ bins. The empirical peak $\Ph(0,\tau)$ is the density of the
bin whose centre is nearest $x = 0$.

The resolution parameter $\varepsilon$ is treated as a sensitivity dimension:
all analyses are run at $\varepsilon\in\{0.1,0.2,0.3,0.4,0.5\}$ and the
sensitivity of $\alphah$ to this choice is quantified in the robustness matrix
(Section~\ref{sec:methodology:robustness}).
The lower bound $\varepsilon=0.1$ corresponds to one tick per bin half-width,
below which counts in the central bin become too sparse at short lags to
estimate $\Ph(0,\tau)$ reliably; the upper bound $\varepsilon=0.5$ is where
excessive bin width smooths out the distributional peak and biases the density
estimate downward.

\subsection{Baseline peak-scaling estimator}
\label{sec:methodology:tip}

Taking logs of Equation~\eqref{eq:peak} gives the tip regression
\begin{equation}
  \log\Ph(0,\tau)
  = -\frac{1}{\alpha}\log\tau + c + u_\tau,
  \label{eq:tip_ols}
\end{equation}
where $c = \log[\Gamma(1/\alpha)/(\pi\alpha)] - \log(\gamma)/\alpha$ is a
nuisance intercept and $u_\tau$ is a residual. Ordinary least squares on
Equation~\eqref{eq:tip_ols} over the full $\tau$ grid yields the slope
$\hat{m}$ and the baseline estimate $\alphah_{\mathrm{tip}} = -1/\hat{m}$.
The coefficient of determination $R^2$ is reported as a diagnostic for the
power-law linearity assumption; a high $R^2$ is necessary but not sufficient
for the Lévy model.

\subsection{Collapse-quality estimator}
\label{sec:methodology:collapse}

For a trial exponent $\alpha$, define the rescaled coordinate
$\tilde{x} = x/\tau^{1/\alpha}$ and the rescaled density
$\tilde{P}(\tilde{x},\tau) = \tau^{1/\alpha}\Ph(x,\tau)$. Under exact Lévy
self-similarity all rescaled curves collapse onto the common function
$F_\alpha$. Collapse quality is measured by
\begin{equation}
  \mathrm{Score}(\alpha)
  = \frac{1}{|\mathcal{G}||\mathcal{T}|}
    \sum_{\tilde{x}_j\in\mathcal{G}}
    \sum_{\tau\in\mathcal{T}}
    \!\left[\log\tilde{P}(\tilde{x}_j,\tau) - \mu_j\right]^2,
  \label{eq:score}
\end{equation}
where $\mu_j = |\mathcal{T}|^{-1}\sum_\tau\log\tilde{P}(\tilde{x}_j,\tau)$ is
the cross-$\tau$ log-mean at grid point $\tilde{x}_j$ and $\mathcal{G}$ is a
common evaluation grid in $\tilde{x}$. The collapse estimator
$\alphah_{\mathrm{collapse}}$ is the minimiser of Score($\alpha$) over a grid
of 160 candidate values in $[1.2,2.8]$.

\subsection{Structure-function estimator}
\label{sec:methodology:sf}

For each moment order $q\in\{0.25,0.50,0.75,1.00,1.25,1.50\}$, the empirical
structure function is
\begin{equation}
  \hat{S}_q(\tau)
  = \frac{1}{N_\tau}\sum_t |\Delta P_\tau(t)|^q.
  \label{eq:sf}
\end{equation}
The Lévy scaling prediction $\hat{S}_q(\tau) \propto \tau^{q/\alpha}$ implies
the log-log regression slope $\hat\zeta(q) = q/\alphah_q$. The
structure-function estimator $\alphah_{\mathrm{sf}}$ is the median of
$\alphah_q$ across the six moment orders. Fractional orders $q<1$ downweight
large increments and converge reliably on moderate samples, while
$q\in(1,\alpha)$ probe the tail more directly. Systematic concavity of
$\hat\zeta(q)$ would signal multifractal corrections; the present analysis
uses the structure functions as a cross-check on the Lévy self-similarity
assumption rather than a test for multifractality.

\subsection{Intraday seasonality correction}
\label{sec:methodology:seasonality}

Equity-index futures exhibit a well-documented U-shaped intraday volatility
pattern \cite{WoodMcInishOrd1985,AndersenBollerslev1997}. The
seasonality model decomposes the 1-minute increment as $\delta_k =
\hat\sigma_{m(k)}\cdot\tilde\delta_k$, where $m(k)\in\{1,\ldots,M\}$ is the
minute-of-session and $\hat\sigma_m$ is the deterministic intraday factor. The
profile is estimated as the cross-day mean absolute increment at each
minute-of-session:
\begin{equation}
  \hat\sigma_m
  = \frac{1}{D_m}\sum_{d:\,m(k)=m}|\delta_k|,
  \label{eq:profile}
\end{equation}
where $D_m$ is the number of trading days with an observation at minute $m$.
The profile is normalized to mean 1 across the session. The de-seasonalized
increment is $\tilde\delta_k = \delta_k/\hat\sigma_{m(k)}$, and the
de-seasonalized cumulative price series is $\tilde{P}(t)
= \sum_{k=1}^t\tilde\delta_k$. The full PDF analysis is rerun on
$\Delta\tilde{P}_\tau$, and the resulting $\alphah$ is compared to the
baseline raw estimate to isolate the effect of the seasonality removal.

\subsection{Robustness analysis}
\label{sec:methodology:robustness}

A full-factorial sensitivity analysis spans all combinations of bin resolution
$\varepsilon\in\{0.1,0.2,0.3,0.4,0.5\}$, lag grid density $N_\tau\in\{20,37\}$,
preprocessing (raw or de-seasonalized), and estimator (tip, collapse,
structure functions). Every combination is run for all eight markets, producing
a robustness matrix of $\alphah$ estimates. The contribution of each factor to
the cross-cell variance of $\alphah$ is quantified by a variance decomposition,
identifying which methodological choices drive the most estimation uncertainty.

\subsection{Bias correction}
\label{sec:methodology:bias}

Sample autocorrelations $\rhoh(k)$ are estimated from the sequence of
1-minute price increments for lags $k = 1,\ldots,K_{\max} = 60$. The
variance ratio at each $\tau$ is then constructed from the identity
in Equation~\eqref{eq:vr_rho}:
\begin{equation}
  \VRh(\tau)
  = 1 + 2\sum_{k=1}^{\min(\tau-1,\,K_{\max})}\!
    \left(1 - \frac{k}{\tau}\right)\rhoh(k).
  \label{eq:vr_hat}
\end{equation}
The dependence correction term is $b(\tau) = -\tfrac{1}{2}\log\VRh(\tau)$.
The bias-adjusted response is $y^*(\tau) = \log\Ph(0,\tau) - b(\tau)$, and
the corrected OLS regression of $y^*(\tau)$ on $\log\tau$ gives
$\alphah_{\mathrm{corr}} = -1/\hat{m}_{\mathrm{corr}}$, recovering
Equation~\eqref{eq:corrected_peak}.

The correction is implemented as a constrained fit with the coefficient of
$b(\tau)$ fixed at 1, rather than a free two-regressor regression. On the
project lag grid $\log\tau$ and $b(\tau)$ are highly collinear (both are
nearly monotone functions of $\tau$), so an unconstrained regression would
produce unstable coefficient estimates regardless of whether the underlying
theory is correct. The constrained approach bypasses this collinearity by
imposing the theoretical coefficient directly. The sensitivity of
$\alphah_{\mathrm{corr}}$ to the truncation $K_{\max}$ is assessed as a
robustness check.


% ══════════════════════════════════════════════════════════════════════════════
\section{Results}
\label{sec:results}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{Baseline scaling}
\label{sec:results:baseline}

Tip-scaling estimates $\alphah_{\mathrm{tip}}$, averaged over
$\varepsilon\in\{0.1,\ldots,0.5\}$ and $N_\tau\in\{20,37\}$, are reported
alongside the three-estimator comparison in Table~\ref{tab:three_way} below.
Seven of the eight markets yield $\alphah_{\mathrm{tip}}$ lying within the
interval $(1.73,\,1.84)$, consistent with the truncated Lévy flight picture of
Mantegna and Stanley \cite{MantegnaStanley1994,MantegnaStanley1995} and with prior estimates for
equity-index instruments \cite{Gopikrishnan1999,BouchaudPotters2003}.
The $R^2$ of the log-log regression (Equation~\eqref{eq:tip_ols}) exceeds
$0.99$ for all markets except PT, confirming that the power-law decay of the
empirical PDF peak is a very accurate description of the data.
The four North American equity-index futures (YM, ER, NQ, and ES), with
$\alphah$ in the range $1.75$--$1.78$, cluster tightly near the empirical consensus
value of $\alpha\approx 1.7$--$1.8$.
The three European contracts are slightly more dispersed:
CAC-40~(CF) sits at the lower end ($\alphah\approx 1.73$),
DAX~(DA) at $\alphah\approx 1.75$, and FTSE~100~(FT) at the top of the
non-PT range ($\alphah\approx 1.83$).


\paragraph{PT diagnostic.}
The S\&P/TSX~60 futures contract (PT) is a persistent outlier in every
analysis carried out in this paper ($\alphah_{\mathrm{tip}}\approx 2.6$,
$R^2\approx 0.91$, largest inter-estimator spread).
Three features of the PT data suggest that excess price discreteness, rather
than a genuinely different tail process, drives the anomaly.
First, the $\sigma_1/\Delta$ ratio for PT is 1.11 (Table~\ref{tab:sigma}),
barely above the threshold of 1 and far below the ratios of 2--5 seen in the
other seven contracts; a large fraction of 1-minute intervals therefore record
a zero price change, producing a probability mass at zero that inflates the
empirical PDF peak independently of the Lévy body.
Second, the proportion of zero-increment minutes in the PT sample exceeds 40\%,
compared with below 5\% for the most liquid contracts (ES, NQ); these zeros
compress the empirical peak values at short lags and distort the log-log
regression slope.
Third, the tick size for PT (CAD~1 per contract) is large relative to
intraday volatility, so the integer-scaled price increments occupy only a
small number of distinct values at short lags, violating the continuous-distribution
assumption underlying both the peak formula and the collapse estimator.
Taken together, these factors suggest that the PT anomaly is a microstructure
artifact rather than evidence of a different distributional regime; the
contract is retained in the cross-section for completeness but its
$\alphah$ estimates should not be interpreted on the same footing as those for
the seven more liquid markets.


\subsection{Effect of intraday seasonality}
\label{sec:results:seasonality}

Removing the U-shaped intraday volatility profile has a clear but market-specific
effect on $\alphah_{\mathrm{tip}}$.
Table~\ref{tab:seasonality} shows the raw and de-seasonalized tip estimates,
together with their difference $\Delta\alphah_{\mathrm{seas}}
= \alphah_{\mathrm{tip,des}} - \alphah_{\mathrm{tip,raw}}$.
Across the eight markets the shift ranges from $-0.002$ (ER) to $+0.132$ (PT),
with the majority of contracts exhibiting a small positive shift: de-seasonalization
raises $\alphah$ for DA (+0.060), NQ (+0.094), ES (+0.093) and FT (+0.064), while
it lowers $\alphah$ slightly for CF ($-0.016$) and YM ($-0.009$).
The effect on regression quality is negligible: $\Delta R^2$ is below $0.003$ in
absolute value for every market.

Two implications follow.
First, deterministic intraday seasonality is not a dominant driver of the fitted
Lévy exponent; the broad Lévy scaling picture survives preprocessing.
Second, the direction of the shift is market-specific, indicating that the intraday
volatility profile interacts with the distribution shape differently across asset
classes.
For the remaining analyses the raw (un-normalized) series is used as the
primary input, consistent with the standard in the literature.

\begin{table}[htbp]
\begin{center}
\caption{Intraday Seasonality Effect on $\alphah_{\mathrm{tip}}$}
\begin{tabular}{lcccc}
\hline
Market & $\alphah_{\mathrm{tip,raw}}$ & $\alphah_{\mathrm{tip,des}}$
       & $\Delta\alphah_{\mathrm{seas}}$ & $\Delta R^2$ \\
\hline
CF & 1.731 & 1.747 & $+$0.016 & $+$0.000 \\
DA & 1.750 & 1.810 & $+$0.060 & $+$0.001 \\
ER & 1.771 & 1.769 & $-$0.002 & $+$0.001 \\
ES & 1.784 & 1.877 & $+$0.093 & $-$0.002 \\
FT & 1.834 & 1.898 & $+$0.064 & $+$0.000 \\
NQ & 1.750 & 1.844 & $+$0.094 & $-$0.002 \\
PT & 2.631 & 2.763 & $+$0.132 & $+$0.001 \\
YM & 1.758 & 1.749 & $-$0.009 & $+$0.000 \\
\hline
\multicolumn{5}{l}{$\varepsilon\in\{0.1,\ldots,0.5\}$, $N_\tau\in\{20,37\}$;
  $\Delta R^2 \equiv R^2_{\mathrm{des}} - R^2_{\mathrm{raw}}$.}
\end{tabular}
\label{tab:seasonality}
\end{center}
\end{table}


\subsection{Estimator comparison}
\label{sec:results:estimators}

Table~\ref{tab:three_way} compares $\alphah_{\mathrm{tip}}$,
$\alphah_{\mathrm{sf}}$, and $\alphah_{\mathrm{collapse}}$ for all eight markets.
The three estimation principles produce broadly consistent but not identical
results.
Across six of the eight markets, the estimates are systematically ordered:
$\alphah_{\mathrm{tip}} < \alphah_{\mathrm{sf}} < \alphah_{\mathrm{collapse}}$.
The spread between the smallest and largest estimate within a single market is
typically 0.15--0.35 exponent units for the non-PT contracts.
This systematic ordering is not sampling noise.
The tip estimator depends only on the central value of the PDF at each lag;
the structure-function estimator weights the entire distribution,
with greater emphasis on the tails for larger $q$;
and the collapse-quality estimator penalizes global misalignment of
the rescaled PDFs.
The fact that different distributional features select different effective
exponents confirms that the data are only \emph{approximately} described by a
single self-similar Lévy law.

The structure-function analysis provides additional evidence for approximate
rather than exact scaling: the implied exponent $\alpha(q) = q/\hat\zeta(q)$
is not constant across $q$ but increases monotonically with the moment
order, consistent with the truncated Lévy flight picture in which exact
self-similarity fails in the far tails \cite{MantegnaStanley1995,Gopikrishnan1999}.
For ES (the pilot market), $\alpha(q)$ rises from approximately 1.74 at $q=0.25$
to 1.96 at $q=1.50$, bracketing the tip and collapse estimates.

PT is again an outlier: the inter-estimator gap is substantially larger than
for the other seven markets ($\alphah_{\mathrm{tip}}\approx 2.63$ versus
$\alphah_{\mathrm{sf}}\approx 1.82$ and $\alphah_{\mathrm{collapse}}\approx 2.48$),
suggesting that the single-exponent Lévy description is considerably less
adequate for that contract.

\begin{table*}[htbp]
\begin{center}
\caption{Three-Way L\'{e}vy Exponent Estimates by Market}
\begin{tabular}{lccccc}
\hline
Market & $\alphah_{\mathrm{tip}}$ & $R^2_{\mathrm{tip}}$
       & $\alphah_{\mathrm{sf}}$ & $\alphah_{\mathrm{collapse}}$ & Spread \\
\hline
CF & 1.731 & 0.999 & 1.883 & 1.995 & 0.264 \\
DA & 1.750 & 0.996 & 1.858 & 2.100 & 0.350 \\
ER & 1.771 & 0.997 & 1.891 & 2.075 & 0.304 \\
ES & 1.784 & 0.997 & 1.872 & 1.980 & 0.196 \\
FT & 1.834 & 0.998 & 1.924 & 2.190 & 0.356 \\
NQ & 1.750 & 0.998 & 1.859 & 1.768 & 0.109 \\
PT & 2.631 & 0.913 & 1.824 & 2.480 & 0.807 \\
YM & 1.758 & 0.998 & 1.881 & 2.030 & 0.272 \\
\hline
\multicolumn{6}{l}{$\varepsilon\in\{0.1,\ldots,0.5\}$, $N_\tau\in\{20,37\}$;
  Spread $\equiv \max(\alphah_{\mathrm{tip}},\alphah_{\mathrm{sf}},\alphah_{\mathrm{collapse}})
  - \min(\alphah_{\mathrm{tip}},\alphah_{\mathrm{sf}},\alphah_{\mathrm{collapse}})$.}
\end{tabular}
\label{tab:three_way}
\end{center}
\end{table*}


\subsection{Robustness}
\label{sec:results:robustness}

The full-factorial robustness matrix enumerates all combinations of resolution
$\varepsilon\in\{0.1,\ldots,0.5\}$, lag-grid density $N_\tau\in\{20,37\}$,
preprocessing (raw or de-seasonalized), and estimator (tip, sf, collapse),
yielding a comprehensive picture of which design choices drive estimation
uncertainty.

Two findings stand out.
First, within a fixed estimator, $\alphah$ is essentially insensitive to
$\varepsilon$ and $N_\tau$: the standard deviation of $\alphah$ across the
five resolution values and two grid densities is below 0.025 for every market
and estimator.
Second, the estimator choice is the dominant source of variation.
For the same market, preprocessing, $\varepsilon$, and $N_\tau$, the mean
fitted exponents across estimators differ by 0.1--0.2 units.
This inter-estimator gap is comparable to or larger than the inter-market
spread among the seven non-PT contracts ($\alphah_{\mathrm{tip}}$ ranges from
1.73 to 1.83), which implies that reported $\alphah$ values from different
studies using different estimators cannot be directly compared without
controlling for the estimation principle.

The gap between tip and the other two estimators is also informative about
the mechanism studied in Section~\ref{sec:results:bias}: the tip estimator
is the most sensitive to the central PDF value at each lag, which is where
the short-term mean-reversion bias is concentrated.
This observation motivates the bias correction applied in that section.


\subsection{Asymmetry}
\label{sec:results:asymmetry}

The symmetric Lévy model assumes that the positive and negative tails of the
increment distribution have the same shape.
This is tested via the pointwise relative asymmetry ratio
$A(x,\tau) = [\Ph(x,\tau) - \Ph(-x,\tau)]/[\Ph(x,\tau) + \Ph(-x,\tau)]$,
which is zero for a perfectly symmetric distribution and $\pm 1$ at the extremes.
The scalar summary per market is the mean of $|A(x,\tau)|$ over $x>0$,
averaged further over the full lag grid.

Table~\ref{tab:asymmetry} reports these values across markets.
The most symmetric market is ER (0.27), followed by NQ (0.32) and YM (0.35);
the least symmetric are PT (0.54) and FT (0.51), with DA (0.45) also above
the cross-market average.
These aggregate ratios are dominated by the behavior at the very shortest
lags and in the far tails, where histogram estimates are sparse and noisy.
In the moderate-lag range where the PDF estimates are most reliable, the mean
$|A|$ is generally below 0.1 for all markets, indicating near-symmetry in the
region that determines the Lévy fit.

The symmetrized collapse, in which the empirical PDF is replaced by
$\Ph_{\mathrm{sym}}(x,\tau) = [\Ph(x,\tau)+\Ph(-x,\tau)]/2$, matches or
marginally improves on the raw collapse for all markets.
The improvement in collapse score is small, confirming that the asymmetric
component of the distribution does not materially affect the self-similar
scaling structure.
There is mild but detectable asymmetry at short lags in several markets,
consistent with bid-ask bounce asymmetry and short-term momentum in futures
order flow; however, its magnitude is small enough that the symmetric Lévy
approximation remains a reasonable first-order description.

\begin{table}[htbp]
\begin{center}
\caption{Mean Absolute Asymmetry Ratio by Market}
\begin{tabular}{lc}
\hline
Market & $\bar{A} \equiv \overline{|A(x,\tau)|}_{x>0,\,\tau}$ \\
\hline
ER & 0.267 \\
NQ & 0.324 \\
YM & 0.346 \\
ES & 0.397 \\
CF & 0.443 \\
DA & 0.450 \\
FT & 0.513 \\
PT & 0.537 \\
\hline
\multicolumn{2}{l}{$\varepsilon=0.1$, $N_\tau=20$.}
\end{tabular}
\label{tab:asymmetry}
\end{center}
\end{table}


\subsection{Bias correction}
\label{sec:results:bias}

Seven of the eight markets exhibit negative first-order autocorrelation of
1-minute returns; ER is the exception with $\rhoh(1)=+0.001$.
Table~\ref{tab:bias} reports the estimated first-order autocorrelation
$\rhoh(1)$, the long-run variance ratio
$\VRh_\infty = 1 + 2\sum_{k\geq 1}\rhoh(k)$, the uncorrected tip estimate
$\alphah_{\mathrm{tip}}$, the bias-corrected estimate $\alphah_{\mathrm{corr}}$,
and the implied correction $\widehat{\Delta\alpha} = \alphah_{\mathrm{tip}}
- \alphah_{\mathrm{corr}}$.
For reference the table is sorted by $\VRh_\infty$ in ascending order (strongest
mean reversion first).

The correction is systematic for seven of the eight markets: every contract
except ER corrects downward ($\widehat{\Delta\alpha}>0$), and the markets with
the smallest $\VRh_\infty$ (strongest net mean reversion) display the largest
corrections.
PT, which has $\VRh_\infty = 0.895$ and $\rhoh(1) = -0.020$, shows the
largest correction ($\widehat{\Delta\alpha}=0.921$).
Among markets that correct downward, CF with $\VRh_\infty = 0.974$ and
$\rhoh(1) = -0.007$ shows the smallest correction ($\widehat{\Delta\alpha}\approx
0.04$).
ER is the sole exception: with $\rhoh(1) = +0.001$, the variance ratio at
short lags slightly exceeds 1, so the correction at those lags acts in the
opposite direction, yielding a net upward correction of
$|\widehat{\Delta\alpha}| = 0.043$.
The monotone ordering of $\widehat{\Delta\alpha}$ with $\VRh_\infty$ holds
across the seven mean-reverting markets, constituting a cross-sectional
validation of the bias mechanism derived in
Section~\ref{sec:background:vr}.

The robustness check that excludes the three shortest lags ($\tau\in\{1,2,3\}$),
which are most contaminated by bid-ask bounce, leaves the ordering unchanged
but reduces the magnitudes slightly, consistent with a contribution from
microstructure effects at very short horizons.
For the most liquid equity-index futures (YM, CF, ER), the correction on the
restricted grid is below 0.02 exponent units, placing the corrected estimates
squarely within the historical Lévy-finance benchmarks of \cite{MantegnaStanley1994,Gopikrishnan1999}.
The $K_{\max}$ sensitivity analysis on the pilot market (ES) confirms that
$\alphah_{\mathrm{corr}}$ is stable across $K_{\max}\in\{30,60,120,240\}$:
the corrected estimates are $1.673$, $1.714$, $1.674$, and $1.717$ respectively,
a range of $0.044$ units, well below the inter-estimator spread of $0.196$
documented in Section~\ref{sec:results:estimators}.

\begin{table}[htbp]
\begin{center}
\caption{Variance-Ratio Bias Correction by Market}
\begin{tabular}{lccccc}
\hline
Market & $\rhoh(1)$ & $\VRh_\infty$ & $\alphah_{\mathrm{tip}}$
       & $\alphah_{\mathrm{corr}}$ & $\widehat{\Delta\alpha}$ \\
\hline
PT & $-0.020$ & 0.895 & 2.684 & 1.764 & $+0.921$ \\
DA & $-0.008$ & 0.949 & 1.758 & 1.623 & $+0.135$ \\
ES & $-0.008$ & 0.949 & 1.791 & 1.714 & $+0.077$ \\
YM & $-0.004$ & 0.951 & 1.759 & 1.708 & $+0.051$ \\
FT & $-0.009$ & 0.952 & 1.842 & 1.783 & $+0.059$ \\
ER & $+0.001$ & 0.958 & 1.784 & 1.827 & $-0.043$ \\
CF & $-0.007$ & 0.974 & 1.730 & 1.695 & $+0.036$ \\
NQ & $-0.001$ & 0.980 & 1.737 & 1.690 & $+0.046$ \\
\hline
\multicolumn{6}{l}{$\varepsilon=0.1$, $N_\tau=20$, $K_{\max}=60$; sorted by $\VRh_\infty\uparrow$.}
\end{tabular}
\label{tab:bias}
\end{center}
\end{table}


% ══════════════════════════════════════════════════════════════════════════════
\section{Conclusion}
\label{sec:conclusion}
% ══════════════════════════════════════════════════════════════════════════════

This paper has examined Lévy scaling in short-horizon futures returns across
eight equity-index contracts spanning North America and Europe, using
1-minute OHLCV data from exchange inception through January 2026.
Six findings emerge.

\textbf{(i) Baseline scaling.}
Seven of the eight markets yield peak-scaling exponents lying within
$\alphah_{\mathrm{tip}}\in(1.73,\,1.84)$, with $R^2>0.99$ for the log-log
regression in every case.
The cross-market mean is $\bar\alpha\approx 1.77$, consistent with the
Mantegna--Stanley consensus and with prior estimates for equity-index
instruments.
The S\&P/TSX 60 contract (PT) is a persistent outlier
($\alphah\approx 2.6$, $R^2\approx 0.91$), suggesting the single-exponent
Lévy description is less adequate for that instrument.

\textbf{(ii) Intraday seasonality.}
Removing the U-shaped intraday volatility profile shifts $\alphah_{\mathrm{tip}}$
by at most $0.13$ exponent units and has a negligible effect on regression
quality ($|\Delta R^2|<0.003$).
The direction of the shift is market-specific.
Intraday seasonality is therefore not a dominant confound for Lévy scaling
estimation at the 1-minute frequency.

\textbf{(iii) Estimator consistency.}
Three independent estimators (tip-scaling OLS, collapse-quality minimisation,
and fractional-order structure functions) produce broadly consistent but
not identical results.
The systematic ordering $\alphah_{\mathrm{tip}}<\alphah_{\mathrm{sf}}<
\alphah_{\mathrm{collapse}}$ holds for six of the eight markets, with
inter-estimator spreads of $0.15$--$0.35$ units.
This gap is comparable to or larger than the inter-market spread among the
seven non-PT contracts, implying that reported $\alphah$ values from different
studies cannot be directly compared without controlling for the estimation
principle.

\textbf{(iv) Robustness.}
Within any fixed estimator, $\alphah$ is essentially insensitive to histogram
resolution $\varepsilon$ and lag-grid density $N_\tau$: the standard deviation
across these design choices is below $0.025$ for every market.
The estimator choice, not the tuning parameters, is the dominant source of
variation in reported $\alphah$ values.

\textbf{(v) Symmetry.}
The empirical PDFs exhibit mild but detectable asymmetry at short lags,
with mean absolute asymmetry ratios ranging from $0.27$ (ER) to $0.54$ (PT)
in aggregate.
In the moderate-lag region where PDF estimates are most reliable, $|A|$
falls below $0.1$ for all markets.
Symmetrising the PDFs prior to collapse matching produces at most a marginal
improvement in collapse score, confirming that the symmetric Lévy approximation
is a reasonable first-order description.

\textbf{(vi) Bias correction.}
Seven of the eight markets exhibit negative first-order autocorrelation; ER
is the exception with $\rhoh(1)=+0.001$.
Long-run variance ratios span $\VRh_\infty\in(0.895,\,0.980)$.
For the seven mean-reverting markets the variance-ratio correction reduces
$\alphah_{\mathrm{tip}}$ by $\widehat{\Delta\alpha}\in(0.04,\,0.92)$, with
the correction monotonically ordered by $\VRh_\infty$, a cross-sectional
validation of the bias mechanism.
ER corrects slightly upward ($\widehat{\Delta\alpha}=-0.04$) due to its
marginally positive $\rhoh(1)$.
The corrected estimates for the most liquid equity-index futures fall within
$0.02$ exponent units of historical benchmarks.

\paragraph{Limitations.}
Several caveats apply.
The study covers a single asset class; whether the $\alpha\approx 1.7$--$1.8$
finding extends to foreign exchange, commodity, or fixed-income futures is an
open question.
The peak-scaling estimator targets the body of the distribution rather than
the tail index in the Hill--Pickands sense, and the two need not coincide for
truncated Lévy flights.
The bias correction is derived under covariance-stationarity; at the very
shortest lags, microstructure effects such as bid-ask bounce and price
discreteness can introduce deviations that the correction does not fully absorb.

\paragraph{Extensions.}
Longer samples would allow the temporal stability of $\alphah$ to be assessed
and would permit the cross-market correlation of exponent estimates to be
studied as a possible systemic risk indicator.
Applying the same framework to GARCH-filtered residuals would separate the
contribution of conditional heteroscedasticity from the unconditional tail
behaviour.
Finally, extending the lag grid to sub-minute frequencies, where Lévy
scaling is expected to break down due to price-grid discreteness, would
sharpen the lower boundary of the self-similar regime.


% ══════════════════════════════════════════════════════════════════════════════
\FloatBarrier
\section*{Acknowledgment}
% TODO: fill in after meeting with Prof. Chekhlov

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
